%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\skillsItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ian Kim} & Email : \href{mailto:iansjk@gmail.com}{iansjk@gmail.com}\\
  \href{http://www.github.com/iansjk}{github.com/iansjk} & Mobile : +1-919-357-4539 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of North Carolina at Chapel Hill}{Chapel Hill, NC}
      {M.S. Speech-Language Pathology, CCC-SLP}{August 2016 -- Dec 2018}
    \resumeSubheading
      {University of North Carolina at Chapel Hill}{Chapel Hill, NC}
      {B.S. Computer Science with Honors, B.A. Linguistics (Phi Beta Kappa, GPA: 3.7)}{August 2009 -- May 2013}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Center for Aphasia and Related Disorders (CARD)}{Chapel Hill, NC}
      {Contract Software Engineer}{Aug 2018 - Present}
      \resumeItemListStart
        \resumeItem{}
        {Designed and developed an iPad app as part of a research study into client-directed cueing for aphasia using \textbf{Ionic, HTML/CSS}, and \textbf{TypeScript}.}
        \resumeItem{}
        {Participated in development and implementation of study protocol, resulting in increase of \textbf{29\%} accuracy at baseline to \textbf{79\%} accuracy at conclusion of study.}
        \resumeItem{}
        {Created a command-line tool in \textbf{Python} using IBM's Watson \textbf{REST/Websocket} API to produce automated judgments of stroke survivors’ speech intelligibility.}
      \resumeItemListEnd

    \resumeSubheading
      {Cheshire Speech and Voice / Wake County Public Schools}{Raleigh, NC}
      {Speech-Language Pathologist Clinical Fellow}{May 2019 -- Jun 2020}
      \resumeItemListStart
        \resumeItem{}
        {Independently developed and carried out speech-language treatment as part of Individualized Education Plans for students in special education.}
        \resumeItem{}
        {Conducted screenings and evaluations of students to identify those with special communication needs.}
        \resumeItem{}
        {Collaborated with parents, teachers, and administrators to identify, troubleshoot, and address academic and functional difficulties.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {UNC Student Stores}{Chapel Hill, NC}
    %   {Tech Shop Associate}{May 2018 -- Aug 2018}
    %   \resumeItemListStart
    %     \resumeItem{}
    %     {Assisted in distribution of Carolina Computing Initiative laptops to incoming new students.}
    %     \resumeItem{}
    %     {Provided assistance to students and families for their technology needs on campus.}
    %   \resumeItemListEnd

    % \resumeSubheading
    %   {Global English Speaking}{Chapel Hill, NC}
    %   {Graduate Research Assistant}{Aug 2018 - Dec 2019}
    %   \resumeItemListStart
    %     \resumeItem{}
    %     {}
    %   \resumeItemListEnd
  
    % \resumeSubheading
    %   {Accent Modification Services}{Chapel Hill, NC}
    %   {Self-Employed}{Jan 2018 - May 2019}
    %   \resumeItemListStart
    %     \resumeItem{}
    %     {}
    %   \resumeItemListEnd
  
    \resumeSubheading
      {UNC-Chapel Hill Center for Cheminformatics Research (CECCR)}{Chapel Hill, NC}
      {Graduate Research Assistant}{Jan 2012 - Jan 2016}
      \resumeItemListStart
        \resumeItem{}
        {Developed Chembench (chembench.mml.unc.edu), a machine learning and drug discovery platform built using \textbf{Java} (\textbf{Tomcat, Struts}).}
        \resumeItem{}
        {Led a transition to using \textbf{Spring DI} and \textbf{Maven} for improved dependency management and maintainability.}
        \resumeItem{}
        {Developed ChemoText, a data mining platform for discovering connections using the NIH PubMed database, utilizing a \textbf{NoSQL} graph database that led to speedups of \textbf{$>$90\%} over existing SQL.}
      \resumeItemListEnd

    \resumeSubheading
      {Social Welfare and Health Informatics Group (SWHIG)}{Chapel Hill, NC}
      {Undergraduate Research Assistant}{Sep 2011 - May 2012}
      \resumeItemListStart
        \resumeItem{}
        {Curated and prepared datasets for the Management Assistance website for North Carolina social welfare programs (ssw.unc.edu/ma) using \textbf{SAS} and \textbf{SQL}.}
      \resumeItemListEnd
    
    \resumeSubheading
      {BlackBerry, Ltd.}{Irving, TX}
      {Java Developer, Student}{May 2011 - Aug 2011}
      \resumeItemListStart
        \resumeItem{}
        {Designed and created Confluence Wiki plugins in \textbf{Java} to extend internal wiki functionality.}  
        \resumeItem{}
        {Created a project progress tracking website using \textbf{Python (Django)}, \textbf{Postgres}, and Web technologies (\textbf{HTML, CSS, jQuery}) to enable more effective collaboration among the Mechanical Engineering team.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \skillsItem
    {Languages}{: \textbf{Java, Python, HTML/CSS, SQL, JavaScript}, TypeScript, R}
    \skillsItem
    {Technologies}{: \textbf{Git, jQuery, Flask}, Django, Travis CI, Heroku, AWS, Ionic, React Native}
    \skillsItem
    {Operating Systems}{: Windows, Linux, Mac OS X}
    \skillsItem
    {Foreign Languages}{: Japanese, Korean}

  \resumeSubHeadingListEnd

%-------------------------------------------

%-----------PUBLICATIONS-----------------
\section{Publications}
  \resumeSubHeadingListStart
    \item{Haley, K. L., Cunningham, K. T., \textbf{Kim, I.}, \& Shafer, J. S. (2019). Autonomy-supportive treatment for acquired apraxia of speech: feasibility and therapeutic effect. \textit{Aphasiology}, 1-21.}
    \item{Capuzzi, S. J., \textbf{Kim, I. S. J.}, Lam, W. I., Thornton, T. E., Muratov, E. N., Pozefsky, D., \& Tropsha, A. (2017). Chembench: a publicly accessible, integrated cheminformatics portal. \textit{Journal of chemical information and modeling}, 57(2), 105-108.}
  \resumeSubHeadingListEnd

\end{document}
